---
title: "Assignment 2: Boulder County House Prices Algorithm"
author: "Gianluca Nelms and Alex Mangiapane"
date: "10/22/2021"
output:bookdown::gitbook:
    code_folding: hide
    fig_caption: yes
    toc: yes
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

# 2. Exploratory Data Analysis 

Currently, we have 24 independent variables to potentially predict house sale prices. To have a have a powerful, undiluted model, we want to narrow down our selection of predictor variables to ones that:
1. Have a significant relationship with the dependent variable ("price"), *and*
2. Are not significantly related to other predictor variables 

To analyze these relationships, we will:
A. Separate variables by data type (e.g. continuous, discrete, binary)
B. Look at Summary Statistics
C. View their distribution with Histograms
D. Plot a few variables with Scatterplots
F. Analyze Correlation Matrices & Independence Tests
E. Map out Variables & the Boulder County Area
G. Choose the final variables

# A. Separate Data Types

It is important to understand and test variables by their data type. Not all data types can be tested with a Pearson Correlation -- but we still need to test their independence. 

``` {r data_types}

vars.ivs.ordinal = c(
  'ele.rank', 'ele.score',
  'build.year.adj', 'build.year',
  'build.quality'
  )

var.df[
  var.df$var_name %in% vars.ivs.ordinal, 
  'data_type'] = 'ordinal'

# FIND BINARY FUNCTION
vars.ivs.binary = 
  apply(boulder.sales %>%
          select(var.ivs.all),
        2,
        function(x) { 
  all(length(unique(
    x[!(is.na(x))]
    ))==2)
    })
vars.ivs.binary = names(vars.ivs.binary[vars.ivs.binary==TRUE])
var.df[
  var.df$var_name %in% vars.ivs.binary, 
  'data_type'] = 'binary'
# # REPLACE TRUE/FALSE with 0/1
# boulder.predict.0 = 
#   boulder.predict.0 %>% 
#     mutate(
#       across(
#         vars.ivs.binary, 
#         ~ifelse(
#           "TRUE",
#           1,
#           0
#         )))

vars.ivs.cont = var.ivs.all[!var.ivs.all %in% 
                         c(vars.ivs.ordinal, vars.ivs.binary)]
var.df[
  var.df$var_name %in% vars.ivs.cont, 
  'data_type'] = 'continuous'
```

# B.	Table of Summary Statistics

The table below summarizes the variables that we are looking at to predict housing prices in Boulder county. These variables do not indicate causal relationship with house prices. Instead, we are investigating if the presence of these observations can correlate to  better predictions of what housing prices could be in the future. 

``` {r table_predict0_vars,  results='asis'}

select_v = function(sf, variable_names=c(var.dv, var.ivs.all)){
  return(sf %>% st_drop_geometry(.) %>%
             select(variable_names))}

select_iv = function(sf, variable_names=var.ivs.all){
  return(sf %>% st_drop_geometry(.) %>%
             select(variable_names))}

tab_num = 1
table_title = glue("Table {tab_num}: Summary Statistics for Boulder County")

stargazer(boulder.predict.0 %>% select_v(.), 
          type="text", digits=1, 
          title=table_title)

```

# C. Histogram

Before correlation tests, it will be important to visualize if their distribution is skewed and what the data looks like. We are also visualizing two statistics to calculate,
1. if the curve's distribution is skewed left or right: |Skewness| > 1
2. if the curve has larger tails than a peak: Kurtosis > 3

``` {r histograms_predict0_vars, warning=FALSE, fig.width=10, fig.height=8}

fig_num = 1

str_remove_vector = function(string, removing) str_remove_all(string, paste(removing, collapse = "|")) %>% str_trim()

skewness = function(vector) sum((vector-mean(vector))^3)/((length(vector)-1)*sd(vector)^3)
# Pearson’s Coefficient of Skewness
# Skewness values and interpretation
## Symmetric:   -0.5 to 0.5
## Moderated:   -1 and -0.5; 0.5 and 1
## Highly:      less than -1; 1

kurtosis = function(vector) sum((vector-mean(vector))^4)/((length(vector)-1)*sd(vector)^4)
# Kurtosis values and interpretation
## Normal Peak (Mesokurtic): 3
## High Peak/Low Tail (Leptokurtic): >3
## Low Peak/High Tail (Platykurtic): <3

plotting = function(
  plot_df = boulder.predict.0, variables = vars.ivs.cont[1], remove_zero=TRUE,
  xlab_remove = c()
  ){
  P = list()
  #vars = names(variables)[!names(variables)%in%c('channel','label')]
  for (cont_var in variables){
    iv_col = plot_df[[cont_var]] %>% na.omit()
    skew = skewness(iv_col) %>% round(2)
    kurt = kurtosis(iv_col) %>% round()
    if(remove_zero==TRUE){
      plot_df = plot_df %>% filter(.data[[cont_var]]>0)
    }
    xlab_var = str_remove_vector(cont_var, xlab_remove) %>% gsub('.',' ', ., fixed=TRUE)
    p =
      ggplot(data=plot_df, aes(x=.data[[cont_var]])) +
        geom_histogram(color='grey50',  stat="count") +
        scale_x_continuous(
          labels=function(lab) ifelse(
            as.numeric(lab)>20000, ifelse(
              as.numeric(lab)>=500000,
              paste(round(as.numeric(lab)/1000000,1),'m',sep=''),
              paste(round(as.numeric(lab)/1000),'k',sep='')),
            lab),
          name = xlab_var
          ) +
        labs(
          title=glue('{cont_var}'), 
          subtitle=glue('Skewness: {skew}, Kurtosis: {kurt}')) + 
        theme(legend.position="none",
              axis.title.y = element_blank()
              ) + plotTheme()
    P = c(P, list(p))
  }
  return(list(plots=P, num=length(vars)))
}

PLOTS = plotting(boulder.predict.0, 
                 vars.ivs.cont %>% sort(), 
                 xlab_remove = c('build','tract'))
hist_plots = ggarrange(plotlist = PLOTS$plots)

annotate_figure(hist_plots, 
                top = text_grob(
                  glue("Figure {fig_num}: Variable Histograms"), 
                  face = "bold", size = 14))

###################

cont_skewed_stats = 
  boulder.predict.0 %>%
  select(vars.ivs.cont) %>%
  st_drop_geometry() %>%
  apply(.,2, skewness)
  
vars.ivs.cont.skew = cont_skewed_stats[abs(cont_skewed_stats)>1] %>% names(.)
var.df[var.df$var_name %in% vars.ivs.cont.skew, 'data_type'] = 'cont_skew'

vars.ivs.cont.notskew = vars.ivs.cont[!vars.ivs.cont %in% vars.ivs.cont.skew]
var.df[var.df$var_name %in% vars.ivs.cont.notskew, 'data_type'] = 'cont_notskew'

```


# D.	Plots of Home Sales Prices & 4 Independent Variables

The below are an example of three predictor variables that we are looking at to assess how well they can be used to predict boulder house sales prices. We expect to observe XXX, XXXX, and XXXX to have a positive relationship with house sales prices.   

These scatter plots also indicate whether the relationship can be predicted using a linear model, or if we need to utilize a different method for better fit. 

```{r plot_predict0_vars}

fig_num = 2

dependent_variable = 'price'

plot_colors= c(
  "blue", "green", "red", "orange"
)

second_max = function(vector){
  vector_mx = max(vector)
  vector_cut = 
  vector[
    vector<vector_mx]
  return(max(vector_cut))
}

ylim_num = max(boulder.predict.0$price)
ylim = second_max(boulder.predict.0$price)

# price_percentiles = ecdf(boulder.predict.0$price)
# if (price_percentiles(max(boulder.predict.0$price))==1){
#   toplim=max(
#     boulder.predict.0[
#       boulder.predict.0$price < toplim,
#       'price'] %>% st_drop_geometry(.))}

scat_vars = c('lot.sqft', 'build.year.adj','build.baths.adj', 'ele.score')
scat_labs = c('Lot Square Footage', 'Build Year (Adjusted)', 'Bathrooms (Adjusted)', 'Elementary Scores')
for (
  variable_number in seq(length(scat_vars))
){
  plot_color = plot_colors[variable_number]
  variable_name = scat_vars[variable_number]
  variable_label = scat_labs[variable_number]
  fm_equation = paste(dependent_variable, "~", variable_name, sep="")
  
  fm = as.formula(fm_equation)
  price_variable = lm(fm, data = boulder.predict.0)
  coefficient = 
    round(
      price_variable$coefficients[variable_name][1], 2)
  
  scat_plot = 
    ggplot(
      data = boulder.predict.0,
      aes(
        x = boulder.predict.0[[variable_name]],
        y = boulder.predict.0$price)) +
    geom_point(size=2, shape=20) +
    labs(title = 
           glue("Figure {fig_num}.{variable_number}: {variable_label}"),
         subtitle = glue("{fm_equation}     Coefficient = ${coefficient %>% count_format()}")
         ) +
    geom_smooth(method = "lm", se=F,
                color = plot_color) +
    xlab(variable_name) +
    ylab("price") +
    ylim(min(boulder.predict.0$price), ylim) + 
    plotTheme()
  print(scat_plot)
}

```

# E.	Correlation & Independence Tests

We will primarily be using a mix of correlation and independence statistical tests in an attempt to measure relationships (1) between predictors & house price, and (2) between the predictors themselves. If there is too much of a relationship between predictor variables then 'multicollinearity' develops -- where it becomes difficult to distinguish which variables are contributing to the model. 

Not every statistical correlation or independence test can be used for ever data type or distribution. For Continuous & Ordinal variables, we will use a correlation matrix with a coefficient that measures the extent to which two variables tend to change together. A Pearson Correlation for Continuous Variables (Figure 2). A Spearman Correlation for Ordinary and Skewed COntinous Variables (Figure 3). For Binary Variables, we will have to use two tests: (Figure 4) a T-Test measuring price & binary predictor and (Figure 5) a Chi-Square Test of Independence between binary predictors. 

Ordinal or Binary variables, for example, shouldn't use the typical Pearson correlation test. We will be following a [statistical test guide from UCLA](https://stats.idre.ucla.edu/other/mult-pkg/whatstat/).

## 1. Continous Variables -- Pearson Correlation

For the Continuous Variables, we will use a Pearson correlation as it measures the linear relationship of the raw data. Any variables with a correlation value greater than 0.8 means they are related to each other. If those related variables are both predictors, then we only need to include one of them -- otherwise we are repeating the same information essentially. 

``` {r corr_cont}
fig_num = 3


ggcorr_full = function(focus_df, #focus_vars= vars, 
                       focus_var = var.dv, corrmethod = 'pearson',
                       title=NULL, subtitle=NULL){
  num = ncol(boulder.cont)
  
  BC = 'white'
  FC = "grey80"
  
  BL = 2
  FL = .2
  RL = 1:num-0.5
  RL[1] = .1
  # RL[num] = .1
  
  library(reshape2)
  
  focus_df.melt = 
    cor(focus_df, method=corrmethod) %>%
    melt()
  
  
  xfaces = focus_df.melt$Var1 %>% as.character() %>% unique()
  yfaces = focus_df.melt$Var2 %>% as.character() %>% unique()
  
  change_focus = function(
    focus_vector, focus, 
    focus_change='bold', unfocus_change='plain'){
    vector = focus_vector[]
    vector[!(vector %in% c(focus))] = unfocus_change
    vector[vector %in% c(focus)] = focus_change
    return(vector)
  }
  
  xfaces = change_focus(xfaces, focus_var)
  yfaces = change_focus(yfaces, focus_var)
  
  focus_df.melt$value = 
    focus_df.melt$value %>%
    round(2)
  
  ggplot(focus_df.melt, aes(Var1, Var2, fill = value)) +
    geom_tile(color = "white") +
    geom_text(
      aes(Var1, Var2, 
          label = gsub("0\\.", "\\.", value)), 
      color = "black", size = 4) +
    scale_fill_gradient2(
      # grey95
      low = "#6D9EC1", mid = "white", high = "#E46726",
      midpoint = 0, limit = c(-1,1), space = "Lab", 
                         name="Pearson\nCorrelation") +
    theme_minimal() +
    coord_fixed() +
    theme(
          axis.text.x = 
            element_text(
              face = xfaces,
              angle=45, vjust=1, hjust=1, 
              margin=margin(-2,0,0,0)),
          # axis.text.x = element_text(margin=margin(-2,0,0,0)),  
          ## Order: top, right, bottom, left  
          axis.text.y = 
            element_text(
              face = yfaces,
              margin=margin(0,-2,0,0)),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          legend.position="none") +
    labs(title = title, subtitle=subtitle) + 
    geom_vline(xintercept=RL, colour=BC, size=BL) +
    geom_hline(yintercept=RL, colour=BC, size=BL) +
    geom_vline(xintercept=RL, colour=FC, size=FL) +
    geom_hline(yintercept=RL, colour=FC, size=FL)}

boulder.cont = 
  boulder.predict.0 %>%
  select(c(var.dv, vars.ivs.cont)) %>% 
  st_drop_geometry(.)

ggcorr_full(boulder.cont,
            title = glue("Figure {fig_num}: Pearson Correlation"),
            subtitle = "Continous Variables"
            )

```



Figure 2 highlights which predictors have a heavier relationship with housing sale prices and each other. A few pairs of predictor variables have high correlations as they are partially the same data: specifically: building livable & above-ground square footage, bathrooms & adjusted bathrooms amounts, and the Census Tract's Population & Unit Densities

For example, the home's livable square footage (build.living.sf = 0.55) and above-ground square footage (build.house.sf = 0.5) have the largest correlation statistic; however, they also have a higher inner-correlation (0.88). We will remove the latter variable (build.house.sf) as it is not as predictive of housing prices.

## 2. Ordinal Variables & Continuous (Skewed Distribution) Variables -- Spearman Correlation

For binary variables and continuous variables with a skewed distribution, we shouldn't perform a pearson linear correlation as a linear . Instead, we can use Spearman's Rank Correlation in Figure 3 as it performs a nonparametric measure of statistic dependence between two variable's rankings.

```{r corr_predict0_vars, fig.width=10}

fig_num = 4

boulder.cont = 
  boulder.predict.0 %>%
  select(c(var.dv, vars.ivs.ordinal, vars.ivs.cont.skew)) %>% 
  st_drop_geometry(.) %>%
  select_if(., is.numeric)

corrmethod = 'spearman'

ggcorrplot(
  cor(boulder.cont, method=corrmethod), #%>% round(2), 
  p.mat = cor_pmat(boulder.cont, lab = TRUE, method = corrmethod),
  colors = c("#6D9EC1", "white", "#E46726"),
  type="lower",
  lab=TRUE) +  
    labs(
      title = glue("Figure {fig_num}: Spearman Correlation"),
      subtitle = "Ordinal Variables & Skewed Continuous Variables")


# boulder.predict.0 %>%
#   select(c('price', 'tract.units.density')) %>%
#   st_drop_geometry() %>%
#   ggplot(., aes(x=tract.units.density, y=price)) + 
#     geom_point()+
#     geom_smooth(method=lm)

```

Figure 3 reaffirms the inner-correlation of some variables

## 3. Binary Variables -- Paired T-Test

to measure difference of price in the variable's binary groups

```{r }

round_str = function(str_num, digits=3) str_num %>% 
        as.numeric() %>%
        round(digits) %>% 
        as.character() %>% 
        str_replace(., "^0\\.", ".") %>%
        str_remove(., "0+$")

round_thresh = function(
  field,
  thresh = .001,
  digits = 3,
  int_check = FALSE,
  commas = FALSE
  ){
  
  if(is.null(field)){return('NULL')}
  if(is.na(field)){return('NA')}
  
  thresh_str = 
    paste('<', round_str(thresh, digits=digits), sep=' ')
  
  field_num = field %>% as.numeric()
  
  field_str = 
    ifelse(
      abs(field_num) < thresh,
      thresh_str,
      ifelse(
        (int_check == TRUE & abs(field_num) >= 1),
        field_num %>% round_str(digits=0),
        field_num %>% round_str(digits=digits)
        ))
  
  return(field_str)
}

```

```{r corr_predict0_vars, fig.width=10}

tab_num = 2

focus_df = boulder.predict.0 %>% st_drop_geometry() %>% select(c(var.dv,vars.ivs.binary))
ttest_df = data.frame()

for (bin_var in vars.ivs.binary){

  bin_df = focus_df %>% select(var.dv, bin_var)
  bin_FALSE = bin_df %>% filter(.data[[bin_var]]==0) %>% pull(var.dv)
  bin_TRUE = bin_df %>% filter(.data[[bin_var]]==1) %>% pull(var.dv)
  
  bin_test = t.test(bin_FALSE, bin_TRUE, alternative = "two.sided")
  
  tstat = bin_test$statistic %>% as.numeric() %>% round(2)
  doff = bin_test$parameter %>% as.numeric() %>% round()
  pval = bin_test$p.value %>% round_thresh(., thresh = .001,  digits = 3)
  mean_FALSE =  paste('$ ', round(mean(bin_FALSE)/1000,0), 'k', sep='')
  mean_TRUE = paste('$ ', round(mean(bin_TRUE)/1000,0), 'k', sep='')
  
  ttest_df = rbind(
    ttest_df,
    c(bin_var, mean_FALSE,mean_TRUE,tstat,doff,pval)
  )}
colnames(ttest_df) = c('iv', "FALSE", "TRUE", "Statistic", "Degrees of Freedom", 'P-Value')

ttest_df %>% 
  kable(., caption = glue("Table {tab_num}: Paired T-Test of Binary Variables")) %>%
  kable_styling() %>%
  add_header_above(
    header=c(' '=1,'Mean Sales Price'=2,'T-Test'=3)
  ) %>%
  footnote(alphabet = 
             c(
               "Two independent samples t-test",
               "significance level: 0.05"
               ))

```

# F. Maps

## 1 Set-Up Plots

``` {r map_functions}

geom_county = function(
  data = boulder.county,
  fill = 'transparent', color='black',
  lwd=1, ...
  ){
    c_plot = geom_sf(data = data, fill = fill, color=color,
          lwd=lwd, ...)
    return(c_plot)}

geom_cities = function(
  data = boulder.cities,
  fill = 'transparent', color='grey',
  lwd=.1, linetype = "dashed",
  ...
  ){
    c_plot = geom_sf(data = data, fill = fill, color=color,
          lwd=lwd,linetype = linetype, ...)
    return(c_plot)}

plot_limits = function(
  data = boulder.cities$geometry,
  # buffer between plot's limits and the geometry 
  # (in unit of geometry column)
  buffer = 0
){
  # creates bounding box
  poly.bbox =
    data %>% st_union() %>%
    # buffers the geometry so the ultimate plot has margins
    st_buffer(buffer) %>%
    st_bbox()
  return(
    # returns the 'coord_sf' function which you can add to any plot
    coord_sf(
      xlim = c(poly.bbox['xmin'], poly.bbox['xmax']),
      ylim = c(poly.bbox['ymin'], poly.bbox['ymax']),
      crs = st_crs(data)
  ))}

st_fishnet = function(focus_sf, cell_size=500){
  focus_union = focus_sf %>% st_union()
  fishnet = 
    st_make_grid(
      focus_union,
      cellsize = cell_size, 
      square = TRUE) %>%
    st_intersection(focus_union) %>%
    st_sf() %>%
    mutate(id.fishnet = rownames(.))}

format_thousand_million = function(lab) 
  ifelse(as.numeric(lab)>20000, 
    ifelse(as.numeric(lab)>=500000,
      paste(round(as.numeric(lab)/1000000,1),'m',sep=''),
      paste(floor(as.numeric(lab)/1000),'k',sep='')),
    lab) %>% 
  str_remove(., "^0+") %>%
  sub("0+$", "", .)

label_breaks = function(
  breaks, combiner = 'to', high_reduce=.1, 
  zero_first = FALSE, above1k = FALSE
  ){
  blen = length(breaks)
  idxs = seq(blen)
  lows  = breaks[idxs[1:blen-1]]
  highs = breaks[idxs[2:blen]] - high_reduce
  highs[length(highs)] = highs[length(highs)] + high_reduce 
  
  if(above1k==TRUE){
    highs = format_thousand_million(highs)
    lows = format_thousand_million(lows)
  }
  
  labels = paste(lows, combiner, highs)
  if(zero_first==TRUE){labels[1] = "0"}
  if(labels[1]=='0 to 0'){labels[1]='0'}
  return(labels)
}

cutting_field = 
  function(var_field, var_breaks) 
    cut(var_field, breaks = var_breaks, dig.lab=10, include.lowest = TRUE)

```

``` {r map_fishnets, fig.width=8.5}

# creating half-mile fishnets

cell_size = .5 * mile

boulder.fishnet = 
  st_fishnet(boulder.county, cell_size=cell_size)

boulder.data = 
  boulder.data %>%
  st_join(
    .,
    boulder.fishnet,
    suffix = c("", ".dupe_join")
  ) %>%
  select(-ends_with(".dupe_join"))

boulder.data.fishnet = 
  merge(
    boulder.fishnet,
    boulder.data %>%
      mutate(
        count.homes = 1,
        count.predicted = ifelse(toPredict=="0", 1, 0),
        count.predicting = ifelse(toPredict=="1", 1, 0)
      ) %>%
      st_drop_geometry() %>%
      group_by(id.fishnet) %>%
      summarize(
        count.homes = sum(count.homes),
        count.predicted = sum(count.predicted),
        count.predicting = sum(count.predicting),
        avg.bedrooms = mean(build.bedrooms),
        avg.baths.adj = mean(build.baths.adj),
        avg.lot.sqft = mean(lot.sqft),
        avg.build.year.adj = mean(build.year.adj) %>%
          round()
      ),
    on='id.fishnet'
  ) %>%
  mutate(
    count.homes = replace_na(count.homes, 0),
    count.predicted = replace_na(count.predicted, 0),
    count.predicting = replace_na(count.predicting, 0)
    )

```


## 2 Map of Home Sales Locations
``` {r map_sales}
map_num = 1

var_field = 'count.homes'
mx = max(boulder.data.fishnet[[var_field]])
focus_length = length(unique(boulder.data.fishnet[[var_field]]))
#var_breaks = seq(0, ceiling_10(mx))
var_breaks = c(0,1,5,15,50, mx)


boulder.data.fishnet$cut.homes = 
  cutting_field(boulder.data.fishnet[[var_field]], var_breaks)
breaks_length = length(unique(boulder.data.fishnet$cut.homes))

#hcl.pals("diverging")
## "qualitative" "sequential" "diverging" "divergingx"
## https://developer.r-project.org/Blog/public/2019/04/01/hcl-based-color-palettes-in-grdevices/
pal = hcl.colors(breaks_length-1, alpha=.95, palette = "PurpOr")
pal = c('grey90',rev(pal))

house_plot = 
  ggplot() +
    geom_sf(data = boulder.data.fishnet, aes(fill = cut.homes), color = NA) +
    scale_fill_manual(
      values = pal, 
      labels = label_breaks(var_breaks),
      name=NULL) + 
    geom_county() + 
    geom_text_sf(sf_to_labels(
      boulder.cities %>% filter(incorporated=='city'), 
      'name')) + 
    labs(title = "All Home Sales") +
    theme(legend.position = "bottom",
        legend.spacing.x = unit(.1, 'in')) +
    mapTheme()

focus_pal = "Teal"
var_field = 'count.predicted'
boulder.data.fishnet$cut.predicted = cutting_field(boulder.data.fishnet[[var_field]], var_breaks)
pal = hcl.colors(breaks_length-1, alpha=.95, palette = focus_pal)
pal = c('grey90',rev(pal))

title = 'Boulder County Housing Sales'

predicted_plot = 
  ggplot() +
    geom_sf(data = boulder.data.fishnet, aes(fill = cut.predicted), color = NA) +
    scale_fill_manual(
      values = pal, 
      labels = label_breaks(var_breaks, zero_first=TRUE),
      name=NULL) + 
    #geom_cities(data=boulder.cities %>% filter(incorporated=='city'), color='grey10', linetype='solid') + 
    geom_county() + 
    geom_text_sf(sf_to_labels(boulder.cities %>% 
                                filter(incorporated=='city'), 'name')) + 
    labs(
      title=title,
      subtitle = glue("Map {map_num}.A. Homes with Known Sales")) +
    theme(legend.position = "bottom",
        legend.spacing.x = unit(.1, 'in')) +
    mapTheme()

focus_pal = "YlOrRd"
var_field = 'count.predicting'
boulder.data.fishnet$cut.predicted = cutting_field(boulder.data.fishnet[[var_field]], var_breaks)
pal = hcl.colors(breaks_length-1, alpha=.95, palette = focus_pal)
pal = c('grey90',pal)

predicting_plot = 
  ggplot() +
    geom_sf(data = boulder.data.fishnet, aes(fill = cut.predicted), color = NA) +
    scale_fill_manual(
      values = pal, 
      labels = label_breaks(var_breaks, zero_first=TRUE),
      name=NULL) + 
    #geom_cities(data=boulder.cities %>% filter(incorporated=='city'), color='grey10') +
    geom_county() + 
    geom_text_sf(sf_to_labels(boulder.cities %>% filter(incorporated=='city'), 'name')) +
    labs(
      title='    ', 
      subtitle = glue("Map {map_num}.B. Homes to Predict Sales"))+ 
    theme(legend.position = "bottom",
        legend.spacing.x = unit(.1, 'in')) +
    mapTheme()


map_grid = plot_grid(predicted_plot, predicting_plot , ncol=2)
map_grid

# draw_label_theme = function(label, theme = NULL, element = "text", ...) {
#   if (is.null(theme)) {theme = ggplot2::theme_get()}
#   if (!element %in% names(theme)) {stop("Element must be a valid ggplot theme element name")}
#   elements = ggplot2::calc_element(element, theme)
#   cowplot::draw_label(
#     label, fontfamily = elements$family, fontface = elements$face,
#     colour = elements$color, size = elements$size, ...)}
#
# title_draw = ggdraw() +
#   draw_label_theme(
#     title, element = "plot.title",
#     x = 0.05, hjust = 0, vjust = 1)
# plot_grid(
#   title_draw, map_grid,
#   ncol = 1,
#   # rel_heights values control vertical title margins
#   rel_heights = c(0.1, 5)
# )

```

## 3 Map of Dependent & Independent Variables
``` {r map_vars}

map_num = 2

boulder.predict.0 = 
  boulder.predict.0 %>%
  st_join(
    .,
    boulder.fishnet,
    suffix = c("", ".dupe_join")
  ) %>%
  select(-ends_with(".dupe_join"))

boulder.predict.fishnet = 
  merge(
    boulder.fishnet,
    boulder.predict.0 %>%
      mutate(count.homes = 1) %>%
      st_drop_geometry() %>%
      group_by(id.fishnet) %>%
      summarize(
        count.homes   = sum(count.homes),
        avg.price     = mean(price),
        avg.bedrooms  = mean(build.bedrooms),
        avg.baths.adj = mean(build.baths.adj),
        avg.lot.sqft  = mean(lot.sqft),
        avg.build.year.adj = mean(build.year.adj) %>%
          round()
      ),
    on='id.fishnet'
  )%>%
  mutate(count.homes = replace_na(count.homes, 0))

var_cut_map = function(
  focus_sf = boulder.predict.fishnet,
  var_field = 'avg.bedrooms',
  focus_pal = "YlOrRd",
  pal_rev = FALSE,
  var_breaks_nomax = c(0,1,2,3, 5),
  var_title = 'Average Bedrooms',
  var_legend = 'Average Bedrooms',
  var_num = 'A'
  ){
  new_var_field = var_field %>% 
    gsub('count','cut', .) %>% gsub('avg','cut', .)
  mx = max(boulder.predict.fishnet[[var_field]]) %>% ceiling()
  focus_length = length(unique(boulder.predict.fishnet[[var_field]]))
  #var_breaks = seq(0, ceiling_10(mx))
  var_breaks = c(var_breaks_nomax, mx)
  boulder.predict.fishnet[[new_var_field]] = 
    cutting_field(boulder.predict.fishnet[[var_field]], var_breaks)
  breaks_length = length(unique(boulder.predict.fishnet[[new_var_field]]))
  var_pal = hcl.colors(breaks_length, #-1, 
                       alpha=.95, palette = focus_pal,
                       rev = pal_rev)
  #var_pal = c('grey90',var_pal)
  
  fish_vars_map = function(focus_sf = boulder.predict.fishnet, cut_field = new_var_field,
                           cut_pal=var_pal, cut_breaks = var_breaks,
                           sub_num='A', map_title = ' ', legend_title=NULL
                           ){
    ggplot() +
      geom_sf(data = focus_sf, aes_string(fill = new_var_field), color = NA) +
      scale_fill_manual(
        values = cut_pal, 
        labels = label_breaks(cut_breaks, high_reduce=ifelse(cut_breaks[1]>0,1,.1), 
                              above1k = ifelse(cut_breaks[1]>10000,TRUE,FALSE)),
        name=legend_title) + 
      #geom_cities(data=boulder.cities %>% filter(incorporated=='city'), color='grey10') +
      geom_county() + 
      geom_text_sf(sf_to_labels(boulder.cities %>% filter(incorporated=='city'), 'name')) +
      labs(
        #title='', 
        subtitle = glue("Map {map_num}.{sub_num}. {map_title}"))+ 
      theme(legend.position = "bottom",
          legend.spacing.x = unit(.1, 'in')) +
      guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
      mapTheme()}
  
  return(fish_vars_map(focus_sf = focus_sf, cut_field = new_var_field,
                cut_pal=var_pal, cut_breaks = var_breaks,
                sub_num=var_num, map_title = var_title, legend_title=var_legend))}

boulder.predict.fishnet$avg.price %>% hist(breaks='fd')
boulder.data$price %>% summary()

Var1_map = var_cut_map(
  var_field = "avg.price",
  focus_pal = "Emrld",
  pal_rev = TRUE,
  var_breaks_nomax = c(50000,250000,500000,1000000, 1500000),
  var_title = 'Average Sales Price',
  var_legend = 'Mean Home Sales\nPrice (USD)',
  var_num = 'A'
)

Var2_map = var_cut_map(
  var_field = 'avg.bedrooms',
  focus_pal = "Red-Purple",
  pal_rev = TRUE,
  var_breaks_nomax = c(0,1,2,3, 5),
  var_title = 'Average Bedrooms',
  var_legend = 'Mean Amount of Bedrooms',
  var_num = 'B'
)

acre = 43560
boulder.predict.fishnet$avg.lot.acre = 
  boulder.predict.fishnet$avg.lot.sqft/acre
boulder.predict.fishnet$avg.lot.acre %>% summary() #hist(breaks='fd')

Var3_map = var_cut_map(
  var_field = 'avg.lot.acre',
  focus_pal = "Heat",
  pal_rev = TRUE,
  var_breaks_nomax = c(0,.2,.5, 1, 2, 5),
  var_title = "Average Lot Size",
  var_legend = 'Mean Lot Size\nin Acres',
  var_num = 'C'
)

Var4_map = var_cut_map(
  var_field = 'avg.build.year.adj',
  focus_pal = "Zissou 1",
  pal_rev = FALSE,
  var_breaks_nomax = c(1900,1940,1980, 2000),
  var_title = "Average Build Year (Adjusted)",
  var_legend = 'Mean Build Year\nAdjusted by Assessor\nafter Major Remodeling',
  var_num = 'D'
)

grid.arrange(
  Var1_map,
  Var2_map,
  Var3_map,
  Var4_map,
  ncol=2
)

```

## 4 Map of Voting Precincts/Neighborhoods 

In a later spatial model test, we will be aggregating housing sales by neighborhoods. This map visualizes the voting precincts we will use like neighborhoods.

``` {r map_nhood}
map_num = 3
ggplot() + 
  # geom_sf(
  #   data = boulder.cities, 
  #   aes(fill=incorporated), 
  #   color='transparent') + 
  geom_sf(
    data = boulder.nhoods, 
    aes(fill=neighborhood), 
    color='transparent',
    lwd=0.1) + 
  scale_fill_hue() + 
  #geom_cities(lwd=0.1, color='grey25') + 
  geom_cities(
    boulder.cities,
    lwd=ifelse(boulder.cities$incorporated=='city', .75,.1), color='grey50', linetype='solid'
    ) + 
  geom_county() + 
  geom_text_sf(sf_to_labels(
    boulder.cities %>% filter(incorporated=='city'), 
    'name')) + 
  theme(legend.position = "none") + 
  labs(title = glue("Map {map_num}. Voting Precincts Map")) + 
  #plot_limits() + 
  mapTheme()

```


# G Choose Final Variables

With the results of our figures, correlation matrices, independence tests, and maps, we can narrow our 24 predictor variables to just 11. The removed variables were mostly too related to other, more potent variables. For example, the amount of rooms 'build.rooms' were too related to number of bathrooms, bedrooms, and living space square footage -- but had a relatively lower Pearson correlation to price. 

``` {r final_vars}

var.ivs = c(
  
  # Continuous
  "lot.sqft",
  "build.living.sf",
  "build.garage.sf",
  "build.bedrooms",
  "build.baths.adj",
  "tract.HH.income",
  
  # ordinal
  "ele.score",
  "build.year.adj",
  "build.quality",
  
  # binary
  "build.hvac",
  "build.bsmt.finished"
  
)
```

-------------------------------