
```{r setup, include=FALSE}
library(bookdown)
knitr::opts_chunk$set(
  echo=TRUE,
  include=TRUE,
  warning=FALSE,
  messages=FALSE,
  fig.width = 8,
  fig.keep = 'all',
  collapse=TRUE
  )
options(tigris_class = "sf")
```


## B.	Table of Summary Statistics
*Present a table of summary statistics with variable descriptions.*

*Sort these variables by their category (internal characteristics, amenities/public services or spatial structure).Check out the `stargazer` package for this.*

Will be using the topredict=0 homes for this Exploratory Data Analysis

```{r summary,  results='asis'}

table_num = 1
table_title = glue("Table {table_num}: Summary Statistics for Boulder County")

boulder.dataSum = boulder.predict.0 %>%
  dplyr:: select(c(price, boulder.dv)) %>%
  st_drop_geometry(.)

stargazer(boulder.dataSum, 
          type="text", digits=1, 
          title=table_title,
          out = "Boulder Data.txt") 
  # kable(.
  #       # , col.names = c("Mean Variables","non-TOD","TOD","non-TOD","TOD"), align="lrrrr"
  #       ) %>%
  #     kable_styling()


```


*(this doesn't need to be in the report, but a method of filtering and transforming non-normally distributed data)*

### Histogram
Plot histograms to assess Normalcy of Data. We don't need to add this in the report, but can be part of data wrangling or feature analysis. ANy that don't appear normal, look at the log transformed 
```{r histograms}
fig_num = 1
variable_name = 'price'
hist(
  boulder.predict.0[[variable_name]], 
  breaks=50, 
  main=glue("Figure {fig_num}.0: {variable_name}"),
  xlab=variable_name)

for (
  variable_number in seq(1,length(boulder.dv), by=1)
){
  #plot_color = plot_colors[variable_number]
  variable_name = boulder.dv[variable_number]
  hist(
    boulder.predict.0[[variable_name]], 
    breaks=50, 
    main=glue("Figure {fig_num}.{variable_number}: {variable_name}"),
    xlab=variable_name)
  }

```


## C.	Correlation Matrix
*Present a correlation matrix*

Correlation matrix to assess multicollinearity
see which variables have positive correlation, which variables have negative correlation, and which ones are correlated above 0.8 or negative 0.8, and if that happens, only choose one

```{r correlation matrix}

fig_num = 2

corrPlotVariables = 
  boulder.predict.0 %>%
  select(boulder.dv) %>% st_drop_geometry(.) %>%
  select_if(., is.numeric)

ggcorrplot(
  round(cor(corrPlotVariables), 1), 
  p.mat = cor_pmat(corrPlotVariables),
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
    labs(
      title = glue("Figure {fig_num}: Boulder Housing Correlation across Numeric Variables")) 

```


### C.2.A log?

```{r log transformed}

# dataset$variable <- log(var)
# 
# 
# dataset$variable <- Log(1+var)) --> #needed if there are any zeros in the dataset

```


### C.2.B log?

```{r histograms of log transformed}
# 
# hist(lnvariables, breaks=50)
# hist(lnvariables, breaks=50)
# .
# .
# .
# hist(lnvariables, breaks=50)
# 
# #if any variables still do not appear normal after log transform, then we will have to deicde if keeping them in or not. Obviously improtant variables (such as dependnet variable ho

```


## D.	Plots of Home Sales Price & 4 Independent Variables
*Present 4 home price correlation scatterplots that you think are of interest.*

*I’m going to look for interesting open data that you’ve integrated with the home sale observations*

Scatterplots of home price correlation that are of interest. 
Looking at interesting open data that we've integrated

```{r scatterplots}

fig_num = 3

plot_colors= c(
  "blue", "green", "red", "orange"
)

second_max = function(vector){
  vector_mx = max(vector)
  vector_cut = 
  vector[
    vector<vector_mx]
  return(max(vector_cut))
}

ylim_num = max(boulder.predict.0$price)
ylim = second_max(boulder.predict.0$price)

# price_percentiles = ecdf(boulder.predict.0$price)
# if (price_percentiles(max(boulder.predict.0$price))==1){
#   toplim=max(
#     boulder.predict.0[
#       boulder.predict.0$price < toplim,
#       'price'] %>% st_drop_geometry(.))}

for (
  variable_number in seq(1,4, by=1)
){
  plot_color = plot_colors[variable_number]
  variable_name = boulder.dv[variable_number]
  
  fm = 
  as.formula(paste(
    'price', "~", variable_name, sep=""))
  price_variable = lm(fm, data = boulder.predict.0)
  coefficient = 
    round(
      price_variable$coefficients[variable_name][1], 2)
  
  scat_plot = 
    ggplot(
      data = boulder.predict.0,
      aes(
        x = boulder.predict.0[[variable_name]],
        y = boulder.predict.0$price)) +
    geom_point(size=2, shape=20) +
    labs(title = 
           glue("Figure {fig_num}.{variable_number}: {variable_name}"),
         subtitle = glue("Coefficient = {coefficient}")
         ) +
    geom_smooth(method = "lm", se=F,
                color = plot_color) +
    xlab(variable_name) +
    ylab("price") +
    ylim(min(boulder.predict.0$price), ylim) + 
    plotTheme()
  print(scat_plot)
}

```


## E.	Map of Dependent Variable (Sales Price)
*Develop 1 map of your dependent variable (sale price)*

### E.1 Map Setup

```{r map_setup}


plot_limits = function(
  poly.geometry = EB.cities$geometry,
  # buffer between plot's limits and the geometry 
  # (in unit of geometry column)
  buffer = 0
){
  # creates bounding box
  poly.bbox =
    poly.geometry %>% st_union() %>%
    # buffers the geometry so the ultimate plot has margins
    st_buffer(buffer) %>%
    st_bbox()
  return(
    # returns the 'coord_sf' function which you can add to any plot
    coord_sf(
      xlim = c(poly.bbox['xmin'], poly.bbox['xmax']),
      ylim = c(poly.bbox['ymin'], poly.bbox['ymax']),
      crs = st_crs(poly.geometry)
  ))}

get_labels = function(
  cut_breaks, round_digit = 0, bucket_diff=1, first_start_range=0, last_end_range=TRUE, input_end_range='', bucket_suffix='', bucket_prefix=''
){
  labels = 
    cut_breaks %>% gsub(",", " to ", .) %>% 
    str_sub(., 2, -2) %>% unique(.)
  
  list_str = function(l, remove=0){
      format(round(as.numeric(l), digit=round_digit)-remove, big.mark=",")}
  
  for (i in seq(from=1,to=length(labels))){
    bucket_range = labels[i] %>% str_split(., " to ")
    
    start_range = paste(bucket_prefix, list_str(bucket_range[[1]][1]))
    end_range = paste(list_str(bucket_range[[1]][2], remove=bucket_diff), bucket_suffix)
    
    if (i == 1 & first_start_range != ''){
      start_range = paste(bucket_prefix, list_str(first_start_range))}
    if (i == length(labels) & input_end_range!=''){
      end_range=paste(list_str(input_end_range), bucket_suffix)
      last_end_range=TRUE
      }
    if (i == length(labels) & last_end_range==FALSE){end_range='+'}
    
    bucket = paste(
        start_range, 
        'to', 
        end_range) %>% str_trim()
    labels[i] = bucket}
    
  return(labels)
  }



plot_vari_spec = function(
  focus_sf  = boulder.predict.0,
  variable  = "price",
  qbreaks   = q5(boulder.predict.0, "price"),
  bucket_diff = 1,
  title     = "Housing Price Variable", 
  subtitle  = "",
  legend_nm = "price",
  caption   = "",
  brewer_colors = 'Spectral',
  round_digit = 0,
  last_end_range = TRUE,
  input_end_range = '',
  bucket_suffix = '',
  buff_col = 'red',
  col_rev = FALSE,
  first_start_range = 0
){

cutting_field = function(var_field, var_breaks){return(var_field %>% cut(., breaks = var_breaks, dig.lab=10, include.lowest = TRUE))}

focus_sf$cut_field = cutting_field(focus_sf[[variable]], qbreaks)
  
cut_breaks = sapply(focus_sf$cut_field, function(brk) brk %>% levels())

labels = get_labels(
  cut_breaks, 
  round_digit = round_digit, bucket_diff = bucket_diff, 
  last_end_range = last_end_range, first_start_range = first_start_range, 
  input_end_range = input_end_range, bucket_suffix = bucket_suffix)

breaks_amount = length(qbreaks)-1
col_vals = brewer.pal(breaks_amount, name = brewer_colors)

if (col_rev==TRUE){col_vals=rev(col_vals)}

return(
ggplot()+
  # geom_sf(data = EB.all, fill=alpha('grey50', .5), color=alpha('grey50', .5)) + 
  # geom_sf(data = EB.back_water, fill=alpha('cornflowerblue', .5), color='transparent') + 
  # geom_sf(data  = EB.cities, fill='grey90')+
  geom_sf(
    data  = focus_sf, 
    aes(fill = cut_field), 
    color='grey50') +
  scale_fill_manual(
    values = col_vals,
    labels = labels, name = legend_nm) +
  # geom_sf(
  #   data=BART.buffers.TOD, fill='transparent', 
  #   color=alpha(buff_col, alpha=.75), lwd=.75) +
  # geom_sf(
  #   data=BART.stops, fill='white',
  #   color='grey30', shape=21) + 
  # geom_text(
  #   data=EB.labels, check_overlap=TRUE,
  #   size = 3.5, fontface='bold', color='black',
  #   aes(x=lon,y=lat, label=label)) + 
  labs(title    = title, 
       subtitle = subtitle,
       caption  = caption) +
  guides(fill = guide_legend(title.position="bottom", 
                             title.hjust = 0.5, title.vjust = 0)) + 
  theme(legend.position = "bottom",
        legend.spacing.x = unit(.1, 'in')) +
  # facet_wrap(~year)+
  mapTheme() #+ plot_limits()
)}

################
```


### E.2 Map of Dependent Variable - Housing Prices 

```{r map of dependent variable}

fig_num = 4



sub_fig_num = 0

variable  = "price"

filt_sf = 
  boulder.predict.0[
    !is.na(boulder.predict.0[[variable]]) &
      !is.infinite(boulder.predict.0[[variable]])
                       ,]
max_variable = max(filt_sf[[variable]])

#breaks = c(0,25,50,100, 150, max_variable)
breaks = seq(0, max_variable, length.out = 5)

plot_vari_spec(
  focus_sf  = filt_sf,
  variable  = variable,
  qbreaks   = breaks,
  title     = glue("Figure {fig_num}.{sub_fig_num} Home Prices"), 
  subtitle  = "",
  caption   = "",
  brewer_colors = 'OrRd',
  legend_nm = "Home Price",
  bucket_suffix = '  ',
  input_end_range = '',
  last_end_range = FALSE,
  round_digit=0,
  bucket_diff=1,
  first_start_range=0
)


# ggplot() +
#   # geom_sf(data = boulder.predict.0, 
#   #         fill = "gray80", color = "white") +
#   # geom_sf(data = boulder.predict.0, 
#   #         fill = "XXXXX", color = "XXXXXX") +
#   geom_sf(data = boulder.predict.0, 
#           aes(color = q5(price))) +
#   scale_color_manual(values = paletteMap) +
#   labs(title = "XXXXXXXX", subtitle = "XXXXXXX") +
#   mapTheme()


```


## F.	Maps of 3 Independent Variables
*Develop 3 maps of 3 of your most interesting independent variables.*
Map of independent Variables - XXXX, XXXX, XXXX, XXXX

```{r map of independent variable}

#maybe we can insert faded base map of boulder county?



for (
  variable_number in seq(1,3, by=1)
){
  plot_color = plot_colors[variable_number]
  variable_name = boulder.dv[variable_number]
  
  fm = 
  as.formula(paste(
    'price', "~", variable_name, sep=""))
  price_variable = lm(fm, data = boulder.predict.0)
  coefficient = 
    round(
      price_variable$coefficients[variable_name][1], 2)
  
  scat_plot = 
    ggplot(
      data = boulder.predict.0,
      aes(
        x = boulder.predict.0[[variable_name]],
        y = boulder.predict.0$price)) +
    geom_point(size=2, shape=20) +
    labs(title = 
           glue("Figure 2.{variable_number}: {variable_name}"),
         subtitle = glue("Coefficient = {coefficient}")
         ) +
    geom_smooth(method = "lm", se=F,
                color = plot_color) +
    xlab(variable_name) +
    ylab("price") +
    ylim(min(boulder.predict.0$price), ylim) + 
    plotTheme()
  print(scat_plot)
  
  variable_map = 
    ggplot() +
    geom_sf(
      data = boulder.predict.0, 
      aes(color =
        q5(boulder.predict.0[[variable_name]]))) +
    scale_color_manual(values = paletteMap) +
    labs(title = "XXXXXXXX", subtitle = "XXXXXXX") +
    mapTheme()
  print(variable_map)
}

# #variable 1
# ggplot() +
#   geom_sf(data = XXXX, fill = "gray80", color = "white") +
#   geom_sf(data = XXXX, fill = "XXXXX", color = "XXXXXX") +
#   geom_sf(data = boulder.predict.0, aes(color = q5(XXXXXX))) +
#   scale_color_manual(values = paletteMap) +
#   labs(title = "XXXXXXXX", subtitle = "XXXXXXX") +
#   mapTheme()
# 
# #variable 2
# ggplot() +
#   geom_sf(data = XXXX, fill = "gray80", color = "white") +
#   geom_sf(data = XXXX, fill = "XXXXX", color = "XXXXXX") +
#   geom_sf(data = boulder.predict.0, aes(color = q5(XXXXX))) +
#   scale_color_manual(values = paletteMap) +
#   labs(title = "XXXXXXXX", subtitle = "XXXXXXX") +
#   mapTheme()
# 
# #variable 3
# ggplot() +
#   geom_sf(data = XXXX, fill = "gray80", color = "white") +
#   geom_sf(data = XXXX, fill = "XXXXX", color = "XXXXXX") +
#   geom_sf(data = boulder.predict.0, aes(color = q5(XXXX))) +
#   scale_color_manual(values = paletteMap) +
#   labs(title = "XXXXXXXX", subtitle = "XXXXXXX") +
#   mapTheme()
# 
# #variable 4
# ggplot() +
#   geom_sf(data = XXXX, fill = "gray80", color = "white") +
#   geom_sf(data = XXXX, fill = "XXXXX", color = "XXXXXX") +
#   geom_sf(data = boulder.predict.0, aes(color = q5(XXXXX))) +
#   scale_color_manual(values = paletteMap) +
#   labs(title = "XXXXXXXX", subtitle = "XXXXXXX") +
#   mapTheme()


```

## G. Assorted Figures
*Include any other maps/graphs/charts you think might be of interest.*


-------------------------------